Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

    By the definitions of $r'$ and $h$, the bottom edge of $r'$ must be contained in $h$. Because $r' = \gbot(\bm{t})$, the bottom edge of $B_\bm{t}$ is contained in the bottom edge of $r'$ and thus also contained in $h$. This means that $h \cap B_{\bm{t}}\neq \emptyset$. On the other hand, the x-range of $h$ must cover that of $r'$ (because $h$ crosses $r'$), which in turn must covers that of $B_\bm{t}$ (because $r'$ covers $B_\bm{t}$). Thus, the x-range of $h$ covers that of $B_\bm{t}$. This together with $h \cap B_{\bm{t}}\neq \emptyset$ tells us that $h$ must cross $B_\bm{t}$.
\end{proof}

>>>>

    By the definitions of $r'$ and $h$, the bottom edge of $r'$ must be contained in $h$ (note that $h$ is one of the segments used to trim $r$ into $r'$). Because $r' = \gbot(\bm{t})$, the bottom edge of $B_\bm{t}$ is contained in the bottom edge of $r'$ and thus also contained in $h$. This means that $h \cap B_{\bm{t}}\neq \emptyset$. On the other hand, the x-range of $h$ must cover that of $r'$ (because $h$ crosses $r'$), which in turn must cover that of $B_\bm{t}$ (because $r'$ covers $B_\bm{t}$). Thus, the x-range of $h$ covers that of $B_\bm{t}$. This together with $h \cap B_{\bm{t}}\neq \emptyset$ tells us that $h$ must cross $B_\bm{t}$.
\end{proof}
